---
title: "Weight of Fish"
author: "Daniel A Soria Z"
date: "summer 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
allthat <- read.csv(file = "Fish.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Perch 

```{r}
perch <- filter(allthat,Species=="Perch")
perch <- select(perch,-1)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

In this perch model we see that the best indicator, would be the two plotsthat help us find the differential in weight would be to use the Height, and Width indicators in this specific perch model.

```{r}
which.max(summary.out$adjr2)
```

This tells us and explains that the best model out of all avilable would be model number 2

```{r}
summary.out$which[2,]
```

From the summary we can see that the best two variables to see were in fact the Height, and Width as proved by this summary.




# Bream 

```{r}
Bream <- filter(allthat,Species=="Bream")
Bream <- select(Bream,-1)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best model that we can see from this one uses Length 2, and Height and Width.

```{r}
which.max(summary.out$adjr2)
```

This allows us to see that the best model would in fact be model number three.

```{r}
summary.out$which[2,]
```

This one tells us that the best two variables to use was Length 2, and Height.

# Smelt 

```{r}
Smelt <- filter(allthat,Species=="Smelt")
Smelt <- select(Smelt,-1)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smelt,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best two variables we can gather from this graph would be Length 2, and Width


```{r}
which.max(summary.out$adjr2)
```

This one tells us that the best one to use would be graph number 4.

```{r}
summary.out$which[2,]
```




